Adopting agile software development in the large organizations: A systematic literature review

### 2014-05-30 journal/article.tex
Work in progress: Coaching, internal coaches

\begin{table}
    \centering
    \begin{tabular}{ >{\raggedright\arraybackslash}p{0.31\textwidth}
                     >{\raggedright\arraybackslash}p{0.61\textwidth} }
        Activity           &  Described in  \\
        \midrule
        Training    &
                P3, P6, P8, P9, P11, P16, P18-P21, P23-P25, P27, P30,
                P32, P35, P37, P39-P41, P43-P46, P48-P51  \\  % 29
        Coaching    &
                P1, P2, P3, P6, P8, P9, P16, P18, P23, P27, P29,
                P33, P36, P39, P40, P41, P45, P46, P47, P50, P52  \\  % 21
        \bottomrule
    \end{tabular}
    \caption{Summary of activities for building awareness and knowledgeability
             in the agile way of working}
    \label{table:transformation_training}
\end{table}

@@

% Coaching was a typical way for steering the agile adoption.
In addition to training, a coaching approach was usually used to teach how to
work in an agile environment. As agile lacks rigorous prescriptions and builds
on human interactions, it is best learned in practice while a coach is giving
advice.

Coaches were driving the agile push [P2, P36], and advocating agile methods [P45].

Coaching was considered very important at project start [P8, P33, P46]. Otherwise
there may be severe long term consequences [P8].

Coaching was also seen as an important success factor [P29, P33].
The coach ensured that transformation would be successful [P16].

Having a impartial third party to rely on was a key success factor [P29].

Having too little coaches [23].

The agile adoption required coaches, especially at the start of agile projects
[P8, P46, P47].

Internal coaches were required for making the change grow [P47].

To be able to coach efficiently it was required that the coach had detailed
understanding of the company's processes and systems [P23]

Coaches were also involved in training [P27].

Scrum masters that had been trained earlier were coaching the teams in some
cases.

As the agile way of working penetrated the organization the need for coaching
was decreasing [P36].

Some cases presented building of a coach community as an integral part of the
agile adoption [P47, P23].

@@

[P39]
* Coach: External support, hired Chief Scrum masters
* How: inspect and adapt

@@

>>>>

\begin{table}
    \centering
    \begin{tabular}{ >{\raggedright\arraybackslash}p{0.31\textwidth}
                     >{\raggedright\arraybackslash}p{0.61\textwidth} }
        Activity           &  Described in  \\
        \midrule
        Training    &
                P3, P6, P8, P9, P11, P16, P18-P21, P23-P25, P27, P30,
                P32, P35, P37, P39-P41, P43-P46, P48-P51  \\  % 29
        Coaching    &
                P1-P3, P6, P8, P9, P11, P16, P18, P23, P27, P29,
                P31-P33, P36, P39-P41, P45-P47, P49, P50, P52  \\  % 25
        Internal personnel is coaching  &
                P2, P3, P6, P11, P16, P23, P29, P31, P32,
                P39, P41, P45, P47, P49, P50, P52  \\    % 16
        \bottomrule
    \end{tabular}
    \caption{Summary of activities for building awareness and knowledgeability
             in the agile way of working}
    \label{table:transformation_training}
\end{table}

@@

% Coaching was a typical way for steering the agile adoption.
% What
In addition to training, a coaching approach was usually used to teach how to
work in an agile environment. As agile lacks rigorous prescriptions and builds
on human interactions, it is best learned in practical situations while a coach
is giving direction.
The main task of coaches was to guide development teams in their daily work.
Some cases described that roles such as the product owner or scrum master
received specialized coaching [P33, P52].
In addition to helping teams, coaches were driving the agile push [P2, P36,
P49], and advocated agile methods in general [P45].

% Why
Coaching was considered necessary, especially in the beginning of agile projects
[P6, P8, P33, P46, 47]. Brown [P8] stated that without adequate coaching there
would have been severe long term consequences [P8]. The application of coaching
was seen as an important success factor [P29, P33], and the job of the coach was
described to be to ensure that the transformation would be successful [P16].
One viewpoint was that the coach was an impartial third party who could be
relied on when resolving transformation impediments [P29].

% Having too little coaches [23].
% Coaches were also involved in training [P27].

% How coaching evolves
As the agile way of working penetrated the organization the need for coaching
was decreasing, and coaching could be reduced [P18, P36]. However, some cases
described that the demand for coaching became permanent in order to keep the
development model healthy and to continuously pursue improvement [P6, P23].
Silva and Doss [P47] describe that internal coaches were required for making the
change grow. Over time the arrangement shifted from having external consultants
as coaches to creating an internal coaching community.

Some cases presented building of a coach community as an integral part of the
agile adoption [P6, P23, P32, P47].

To be able to coach efficiently it was required that the coach had detailed
understanding of the company's processes and systems [P23, P39].

The maturity of coaches grew over time [P32].

% Scrum masters that had been trained earlier were coaching the teams in some
% cases.

@@

[P39]
* Coach: External support, hired Chief Scrum masters
* How: inspect and adapt
* Particular: Internal coaches had better understanding of the company's procedures

@@

% Inhouse coaching

What?

Why?

Benefits?

Differences?

[P2]
* Why: There were too few coaches, so new ones were trained internally

[P3]
* Benefit: The internal coaches were accessible. You could easily acquire coaching for your team

[P6]
* What: There is a train the trainer program
* Why: Coaches can be expensive, more coaches can scale up agile more quickly

[P9]
* There was a lack of qualified coaches
* Why: hiring good external coaches was difficult
* It was hard to make the internal coaching resources work as well

[P11]
* Coaches: The Scrum masters served as internal coaches

[P16]
* Coaches: The roll-out team coached

[P23]
* A coach community evolved
* Why: The organization was so large
* How: Paired coaching

[P31]
* A certain person was hiread as senior agile coach, and he stayed through out the transformation
* Coach: A person was hired permanently

[P32]
* Particular: The maturity of coaches grew over time
* Why: There were so many people to educate

[P39]
* Benefit: Internal coaches had understanding of procedures and communication policies

[P45]
* What: After 8 months the coaches started training future Scrum mentors

[P47]
* Why: There was an internal need. It just was necessary to have coaches.
* How: First there were some external coaches, then an internal community was built
* Coaches: People who were passionate to teach agile

[P49]
* Why: To scale up agile implementation
* Why: The internal coaches create the change
